Enhancement of SDR in Thessaloniki

### 2024-02-29 GHI_enh_04_investigate.tex
Commit 2024-02-29 15:11

@@

\begin{verbatim}
2024-02-29 11:01:18.2 athan@tyler GHI_enh_04_investigate.R 1.255829 mins
\end{verbatim}

>>>>

\begin{verbatim}

Attaching package: 'dplyr'
\end{verbatim}

    between, first, last
\end{verbatim}

\begin{verbatim}
The following objects are masked from 'package:stats':

    filter, lag
\end{verbatim}

    intersect, setdiff, setequal, union
\end{verbatim}

\begin{verbatim}
Loading required package: viridisLite
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-6} \end{center}

@@

\begin{verbatim}
2024-02-29 13:02:09.3 athan@tyler GHI_enh_04_investigate.R 0.985446 mins
\end{verbatim}
